---
title: "ABM_Results"
author: "Stine Fabech Hansson"
date: "23/11/2020"
output:  
  md_document:
    variant: markdown_github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Packages
```{r}
library(pacman)
p_load(tidyverse)
p_load(splitstackshape)

setwd("C:/Users/stine/OneDrive/Cognitive Science/5th_Semester/bachelor/ABM_Aarhus")
```

Import csv
```{r}
base_sim_1 <- read_csv2("base_sim_1.csv")
colnames(base_sim_1) <- "temporary"

base_sim_1 <- cSplit(base_sim_1, "temporary", ",")

colnames(base_sim_1) <- c("agent_type","equally_good_1","original_postcode","move_1","move_2","move_3","move_4","move_5","move_6")



base_sim_2 <- read_csv2("building_sim_1.csv") 
colnames(base_sim_2) <- "temporary"

base_sim_2 <- cSplit(base_sim_2, "temporary", ",")

colnames(base_sim_2) <- c("agent_type","equally_good_1","original_postcode","move_1","move_2","move_3","move_4","move_5","move_6")


base_sim_3 <- read_csv2("int_sim_1.csv")
colnames(base_sim_3) <- "temporary"

base_sim_3 <- cSplit(base_sim_3, "temporary", ",")

colnames(base_sim_3) <- c("agent_type","equally_good_1","original_postcode","move_1","move_2","move_3","move_4","move_5","move_6")

```

Make a column with all the postcodes that each agent ends up in 
```{r}

# MAke column with all the last choices (moves where the element to the right of them is NA)
i=1
the_last <- function(x){
  x$last_move <- NA
  for(i in 1:nrow(x)){
  x$last_move[i] <-  x[i,max(which(!is.na(x[i,])))]
  }
  return(x)
}

base_sim_1 <- the_last(base_sim_1)

base_sim_2 <- the_last(base_sim_2)

base_sim_3 <- the_last(base_sim_3)
```

Finding the number of agents that end up living in each postcode
```{r}
# Use group_by and count to count how many people live in each postcode (both for original Postcode column and the newly created column)
original_living_count <- aggregate(base_sim_1$original_postcode, by=list(base_sim_1$original_postcode), FUN=length)
last_move_count <-aggregate(base_sim_1$last_move, by=list(base_sim_1$last_move), FUN=length)



original_living_count_2 <- aggregate(base_sim_2$original_postcode,
                                     by=list(base_sim_2$original_postcode), FUN=length)
last_move_count_2 <-aggregate(base_sim_2$last_move,
                              by=list(base_sim_2$last_move), FUN=length)




original_living_count_3 <- aggregate(base_sim_3$original_postcode,
                                     by=list(base_sim_3$original_postcode), FUN=length)
last_move_count_3 <- aggregate(base_sim_3$last_move, by=list(base_sim_3$last_move), FUN=length)
```

Making the number of agents in each postcode stand in column with all postcodes. 
Postcodes without any agents in are = 0
```{r}
######## OVERVIEW #########
envi <- read_csv2("environment_aarhus.csv")
envi <- envi[,-c(1, 4:5)]

overview <- data.frame(Postcode = envi$Postalcodes)
overview$base_line = NA

i=1
ordering <- function(over, last){
  for (i in 1:length(over$Postcode)){
    if(over$Postcode[i] %in% last$Group.1){
      filt <- filter(last, over$Postcode[i] == last$Group.1)
      over$base_line[i] <- filt$x
    } else if(!over$Postcode[i] %in% last$Group.1){
    over$base_line[i] <- 0
    }
  }
  return(over)
} 

overview_1 <- ordering(over = overview, last = last_move_count)

overview_2 <- ordering(over = overview, last = last_move_count_2)

overview_3 <- ordering(over = overview, last = last_move_count_3)



```

Number of agent_types that live in each postcode
```{r}
# See what agent-types live in each postcode 
by_type_move_count_1 <- aggregate(base_sim_1$last_move, by=list(base_sim_1$last_move,
                                                                base_sim_1$agent_type), FUN=length)

by_type_move_count_2 <- aggregate(base_sim_2$last_move,
                                  by=list(base_sim_2$last_move,
                                          base_sim_2$agent_type), FUN=length)

by_type_move_count_3 <- aggregate(base_sim_3$last_move, by=list(base_sim_3$last_move,
                                                                    base_sim_3$agent_type), FUN=length)
```

## Dividing the df up into one for each agent type
```{r}
total_over_under_18 <-  read_csv("total_over_under_18.csv")

sim_base_kids_high <- by_type_move_count_1 %>% filter(Group.2 == "kids_high_economy")
sim_base_kids_high <- ordering(overview_1, sim_base_kids_high)

sim_base_kids_high$dif_vs_real <- NA
sim_base_kids_high$dif_vs_real <-  abs(total_over_under_18$`Total non-western households` - sim_base_kids_high$base_line)
mean(sim_base_kids_high$dif_vs_real)
#write.csv(sim_base_kids_high, "results_base_kids_high.csv", row.names = FALSE)


sim_base_no_high <- by_type_move_count_1 %>% filter(Group.2 == "no_kids_high_economy")
sim_base_no_high <- ordering(overview_1, sim_base_no_high)

sim_base_no_high$dif_vs_real <- NA
sim_base_no_high$dif_vs_real <-  abs(total_over_under_18$`Total non-western households` - sim_base_no_high$base_line)
mean(sim_base_no_high$dif_vs_real)
#write.csv(sim_base_no_high, "results_base_no_high.csv", row.names = FALSE)


sim_base_kids_low <- by_type_move_count_1 %>% filter(Group.2 == "kids_low_economy")
sim_base_kids_low <- ordering(overview_1, sim_base_kids_low)

sim_base_kids_low$dif_vs_real <- NA
sim_base_kids_low$dif_vs_real <-  abs(total_over_under_18$`Total non-western households` - sim_base_kids_low$base_line)
mean(sim_base_kids_low$dif_vs_real)
#write.csv(sim_base_kids_low, "results_base_kids_low.csv", row.names = FALSE)



sim_base_no_low <- by_type_move_count_1 %>% filter(Group.2 == "no_kids_low_economy")
sim_base_no_low <- ordering(overview_1, sim_base_no_low)

sim_base_no_low$dif_vs_real <-  abs(total_over_under_18$`Total non-western households` - sim_base_no_low$base_line)
mean(sim_base_no_low$dif_vs_real)
#write.csv(sim_base_no_low, "results_base_no_low.csv", row.names = FALSE)
```


Comparing it with the actual number of people in each postcode 
```{r}
############# COMPARING base simulation with number in real life ###############
total_over_under_18 <-  read_csv("total_over_under_18.csv")
overview_1$dif_vs_real <- NA
overview_1$dif_vs_real <-  abs(total_over_under_18$`Total non-western households` - overview_1$base_line)
mean(overview_1$dif_vs_real)
#write.csv(overview_1, "results_base_1.csv", row.names = FALSE)


################################# Comparing build sim with base sim ####################
overview_2$dif_vs_base <- NA
overview_2$dif_vs_base <-  abs(overview_1$base_line - overview_2$base_line)
mean(overview_2$dif_vs_base) # Average difference between base and int simulation
#write.csv(overview_2, "results_build_1.csv", row.names = FALSE)



################################# Comparing int sim with base sim ####################
overview_3$dif_vs_base <- NA
overview_3$dif_vs_base <-  abs(overview_1$base_line - overview_3$base_line)
mean(overview_3$dif_vs_base) # Average difference between base and int simulation
#write.csv(overview_3, "results_int_1.csv", row.names = FALSE)

```

Creating total df 
```{r}

over_18 <- read_csv2("indvandrere_aarhus_over_18.csv")
over <- as.matrix(over_18[1:22,3:7])
over <- cbind(over, over[,1]+over[,2]+over[,3]+over[,4]+over[,5]) #creating total column 


under_18 <- read_csv2("indvandrere_aarhus_under_18.csv")
under <- as.matrix(under_18[1:22,3:7])
under <- cbind(under, under[,1]+under[,2]+under[,3]+under[,4]+under[,5])


total_over_under_18 <- over + under # Creating matrix with total amount of people 
total_over_under_18 = cbind(total_over_under_18, total_over_under_18[,2] + total_over_under_18[,4]) # Column with total amount of non-western 
total_over_under_18 =  cbind(total_over_under_18, round(total_over_under_18[,7]/2.5))

total_over_under_18 <- cbind(over_18$Postnummer[1:22], total_over_under_18)

#Change column names 
colnames(total_over_under_18) <- c("Postcode", "Danish origin", "Descendants from non_western countries", "Descendants from western countries", "Immigrants from non-western countries", "Immigrants from western countries", "In total", "Total non-western", "Total non-western households")

total_over_under_18 <- as.data.frame(total_over_under_18)

#write.csv(total_over_under_18, "total_over_under_18.csv", row.names = FALSE)



```

