---
title: "plots_ABM"
author: "Stine Fabech Hansson"
date: "27/11/2020"
output:   
  md_document:
    variant: markdown_github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load Packages
```{r}
library(pacman)
p_load(tidyverse)
p_load(sf, lwgeom)
p_load(ggplot2)
p_load(sp)
p_load(rgdal)
p_load(broom)
p_load(maptools)
p_load(gridExtra)
p_load(patchwork)
```


################################## MAP Plots ################################

Fix the jumbled data in gg so that each postcode can be matched with a number of households:
```{r}

#adds the number of immigrants that ends up in each postcode in simulation
add_sim_to_gg <- function(gg_object, overview){
  
  gg_object$data$number_immigrants <- NA
  gg_object$data$postcode <- NA
  gg_object$data$number_immigrants[1:33] <-
   overview$base_line[overview$POSTNR_TXT==8380]
  gg_object$data$postcode[1:33] <- 8380
  
  gg_object$data$number_immigrants[34:64] <-
    overview$base_line[overview$POSTNR_TXT==8310]
  gg_object$data$postcode[34:64] <- 8310
  
  gg_object$data$number_immigrants[65:125] <-
    overview$base_line[overview$POSTNR_TXT==8340]
  gg_object$data$postcode[65:125] <- 8340
  
  gg_object$data$number_immigrants[126:170] <-
    overview$base_line[overview$POSTNR_TXT==8270]
  gg_object$data$postcode[126:170] <- 8270
  
  gg_object$data$number_immigrants[171:200] <- 
    overview$base_line[overview$POSTNR_TXT==8330]
  gg_object$data$postcode[171:200] <- 8330
  
  gg_object$data$number_immigrants[201:243] <- 
    overview$base_line[overview$POSTNR_TXT==8530]
  gg_object$data$postcode[201:243] <- 8530
  
  gg_object$data$number_immigrants[244:267] <- 
    overview$base_line[overview$POSTNR_TXT==8320]
  gg_object$data$postcode[244:267] <- 8320 
  
  gg_object$data$number_immigrants[245:296] <-
    overview$base_line[overview$POSTNR_TXT==8462]
  gg_object$data$postcode[245:296] <- 8462 
  
  gg_object$data$number_immigrants[297:321] <- 
     overview$base_line[overview$POSTNR_TXT==8230]
  gg_object$data$postcode[297:321] <-8230
  
  gg_object$data$number_immigrants[322:353] <-
    overview$base_line[overview$POSTNR_TXT==8381]
  gg_object$data$postcode[322:353] <-8381
  
  
  gg_object$data$number_immigrants[354:395] <-
     overview$base_line[overview$POSTNR_TXT==8250]
  gg_object$data$postcode[354:395] <- 8250
    
  gg_object$data$number_immigrants[396:422] <-
    overview$base_line[overview$POSTNR_TXT==8361]
  gg_object$data$postcode[396:422] <- 8361
  
  gg_object$data$number_immigrants[423:462] <- 
    overview$base_line[overview$POSTNR_TXT==8260]
  gg_object$data$postcode[423:462] <- 8260
  
  gg_object$data$number_immigrants[463:544] <- 
    overview$base_line[overview$POSTNR_TXT==8000]
  gg_object$data$postcode[463:544] <- 8000
  
  gg_object$data$number_immigrants[545:579] <-
    overview$base_line[overview$POSTNR_TXT==8355]
  gg_object$data$postcode[545:579] <- 8355
  
  gg_object$data$number_immigrants[580:608] <-
    overview$base_line[overview$POSTNR_TXT==8520]
  gg_object$data$postcode[580:608] <- 8520
  
  gg_object$data$number_immigrants[609:651] <-
    overview$base_line[overview$POSTNR_TXT==8471]
  gg_object$data$postcode[609:651] <- 8471
    
  gg_object$data$number_immigrants[652:684] <-
    overview$base_line[overview$POSTNR_TXT==8200]
  gg_object$data$postcode[652:684] <- 8200
    
  gg_object$data$number_immigrants[685:737] <-
    overview$base_line[overview$POSTNR_TXT==8541]
  gg_object$data$postcode[685:737] <- 8541
    
  gg_object$data$number_immigrants[738:761] <- 
    overview$base_line[overview$POSTNR_TXT==8541] 
  gg_object$data$postcode[738:761] <- 8541
  
  gg_object$data$number_immigrants[762:792] <-
    overview$base_line[overview$POSTNR_TXT==8240]
  gg_object$data$postcode[762:792] <- 8240
  
  gg_object$data$number_immigrants[793:816] <-
    overview$base_line[overview$POSTNR_TXT==8210]
  gg_object$data$postcode[793:816] <- 8210
  
  gg_object$data$number_immigrants[817:846] <- 
    overview$base_line[overview$POSTNR_TXT==8220]
  gg_object$data$postcode[817:846] <- 8220
  
  return(gg_object)
}

#Adds the difference between real and simulated data (accuracy) 
add_abs_diff_to_base_gg <- function(gg_object, overview){
  
  gg_object$data$abs_diff_real_sim <- NA
  gg_object$data$postcode <- NA
  
  gg_object$data$abs_diff_real_sim[1:33] <-
   overview$dif_vs_real[overview$POSTNR_TXT==8380]
  gg_object$data$postcode[1:33] <- 8380
  
  gg_object$data$abs_diff_real_sim[34:64] <-
    overview$dif_vs_real[overview$POSTNR_TXT==8310]
  gg_object$data$postcode[34:64] <- 8310
  
  gg_object$data$abs_diff_real_sim[65:125] <-
    overview$dif_vs_real[overview$POSTNR_TXT==8340]
  gg_object$data$postcode[65:125] <- 8340
  
  gg_object$data$abs_diff_real_sim[126:170] <-
    overview$dif_vs_real[overview$POSTNR_TXT==8270]
  gg_object$data$postcode[126:170] <- 8270
  
  gg_object$data$abs_diff_real_sim[171:200] <- 
    overview$dif_vs_real[overview$POSTNR_TXT==8330]
  gg_object$data$postcode[171:200] <- 8330
  
  gg_object$data$abs_diff_real_sim[201:243] <- 
    overview$dif_vs_real[overview$POSTNR_TXT==8530]
  gg_object$data$postcode[201:243] <- 8530
  
  gg_object$data$abs_diff_real_sim[244:267] <- 
    overview$dif_vs_real[overview$POSTNR_TXT==8320]
  gg_object$data$postcode[244:267] <- 8320 
  
  gg_object$data$abs_diff_real_sim[245:296] <-
    overview$dif_vs_real[overview$POSTNR_TXT==8462]
  gg_object$data$postcode[245:296] <- 8462 
  
  gg_object$data$abs_diff_real_sim[297:321] <- 
     overview$dif_vs_real[overview$POSTNR_TXT==8230]
  gg_object$data$postcode[297:321] <-8230
  
  gg_object$data$abs_diff_real_sim[322:353] <-
    overview$dif_vs_real[overview$POSTNR_TXT==8381]
  gg_object$data$postcode[322:353] <-8381
  
  
  gg_object$data$abs_diff_real_sim[354:395] <-
     overview$dif_vs_real[overview$POSTNR_TXT==8250]
  gg_object$data$postcode[354:395] <- 8250
    
  gg_object$data$abs_diff_real_sim[396:422] <-
    overview$dif_vs_real[overview$POSTNR_TXT==8361]
  gg_object$data$postcode[396:422] <- 8361
  
  gg_object$data$abs_diff_real_sim[423:462] <- 
    overview$dif_vs_real[overview$POSTNR_TXT==8260]
  gg_object$data$postcode[423:462] <- 8260
  
  gg_object$data$abs_diff_real_sim[463:544] <- 
    overview$dif_vs_real[overview$POSTNR_TXT==8000]
  gg_object$data$postcode[463:544] <- 8000
  
  gg_object$data$abs_diff_real_sim[545:579] <-
    overview$dif_vs_real[overview$POSTNR_TXT==8355]
  gg_object$data$postcode[545:579] <- 8355
  
  gg_object$data$abs_diff_real_sim[580:608] <-
    overview$dif_vs_real[overview$POSTNR_TXT==8520]
  gg_object$data$postcode[580:608] <- 8520
  
  gg_object$data$abs_diff_real_sim[609:651] <-
    overview$dif_vs_real[overview$POSTNR_TXT==8471]
  gg_object$data$postcode[609:651] <- 8471
    
  gg_object$data$abs_diff_real_sim[652:684] <-
    overview$dif_vs_real[overview$POSTNR_TXT==8200]
  gg_object$data$postcode[652:684] <- 8200
    
  gg_object$data$abs_diff_real_sim[685:737] <-
    overview$dif_vs_real[overview$POSTNR_TXT==8541]
  gg_object$data$postcode[685:737] <- 8541
    
  gg_object$data$abs_diff_real_sim[738:761] <- 
    overview$dif_vs_real[overview$POSTNR_TXT==8541] 
  gg_object$data$postcode[738:761] <- 8541
  
  gg_object$data$abs_diff_real_sim[762:792] <-
    overview$dif_vs_real[overview$POSTNR_TXT==8240]
  gg_object$data$postcode[762:792] <- 8240
  
  gg_object$data$abs_diff_real_sim[793:816] <-
    overview$dif_vs_real[overview$POSTNR_TXT==8210]
  gg_object$data$postcode[793:816] <- 8210
  
  gg_object$data$abs_diff_real_sim[817:846] <- 
    overview$dif_vs_real[overview$POSTNR_TXT==8220]
  gg_object$data$postcode[817:846] <- 8220
  
  return(gg_object)
}

#Adds the difference between simulations with restrictions and base simulation  
add_abs_diff_to_rest_gg <- function(gg_object, overview){
  
  gg_object$data$abs_diff_base_sim <- NA
  gg_object$data$postcode <- NA
  
  gg_object$data$abs_diff_base_sim[1:33] <-
   overview$dif_vs_base[overview$POSTNR_TXT==8380]
  gg_object$data$postcode[1:33] <- 8380
  
  gg_object$data$abs_diff_base_sim[34:64] <-
    overview$dif_vs_base[overview$POSTNR_TXT==8310]
  gg_object$data$postcode[34:64] <- 8310
  
  gg_object$data$abs_diff_base_sim[65:125] <-
    overview$dif_vs_base[overview$POSTNR_TXT==8340]
  gg_object$data$postcode[65:125] <- 8340
  
  gg_object$data$abs_diff_base_sim[126:170] <-
    overview$dif_vs_base[overview$POSTNR_TXT==8270]
  gg_object$data$postcode[126:170] <- 8270
  
  gg_object$data$abs_diff_base_sim[171:200] <- 
    overview$dif_vs_base[overview$POSTNR_TXT==8330]
  gg_object$data$postcode[171:200] <- 8330
  
  gg_object$data$abs_diff_base_sim[201:243] <- 
    overview$dif_vs_base[overview$POSTNR_TXT==8530]
  gg_object$data$postcode[201:243] <- 8530
  
  gg_object$data$abs_diff_base_sim[244:267] <- 
    overview$dif_vs_base[overview$POSTNR_TXT==8320]
  gg_object$data$postcode[244:267] <- 8320 
  
  gg_object$data$abs_diff_base_sim[245:296] <-
    overview$dif_vs_base[overview$POSTNR_TXT==8462]
  gg_object$data$postcode[245:296] <- 8462 
  
  gg_object$data$abs_diff_base_sim[297:321] <- 
     overview$dif_vs_base[overview$POSTNR_TXT==8230]
  gg_object$data$postcode[297:321] <-8230
  
  gg_object$data$abs_diff_base_sim[322:353] <-
    overview$dif_vs_base[overview$POSTNR_TXT==8381]
  gg_object$data$postcode[322:353] <-8381
  
  
  gg_object$data$abs_diff_base_sim[354:395] <-
     overview$dif_vs_base[overview$POSTNR_TXT==8250]
  gg_object$data$postcode[354:395] <- 8250
    
  gg_object$data$abs_diff_base_sim[396:422] <-
    overview$dif_vs_base[overview$POSTNR_TXT==8361]
  gg_object$data$postcode[396:422] <- 8361
  
  gg_object$data$abs_diff_base_sim[423:462] <- 
    overview$dif_vs_base[overview$POSTNR_TXT==8260]
  gg_object$data$postcode[423:462] <- 8260
  
  gg_object$data$abs_diff_base_sim[463:544] <- 
    overview$dif_vs_base[overview$POSTNR_TXT==8000]
  gg_object$data$postcode[463:544] <- 8000
  
  gg_object$data$abs_diff_base_sim[545:579] <-
    overview$dif_vs_base[overview$POSTNR_TXT==8355]
  gg_object$data$postcode[545:579] <- 8355
  
  gg_object$data$abs_diff_base_sim[580:608] <-
    overview$dif_vs_base[overview$POSTNR_TXT==8520]
  gg_object$data$postcode[580:608] <- 8520
  
  gg_object$data$abs_diff_base_sim[609:651] <-
    overview$dif_vs_base[overview$POSTNR_TXT==8471]
  gg_object$data$postcode[609:651] <- 8471
    
  gg_object$data$abs_diff_base_sim[652:684] <-
    overview$dif_vs_base[overview$POSTNR_TXT==8200]
  gg_object$data$postcode[652:684] <- 8200
    
  gg_object$data$abs_diff_base_sim[685:737] <-
    overview$dif_vs_base[overview$POSTNR_TXT==8541]
  gg_object$data$postcode[685:737] <- 8541
    
  gg_object$data$abs_diff_base_sim[738:761] <- 
    overview$dif_vs_base[overview$POSTNR_TXT==8541] 
  gg_object$data$postcode[738:761] <- 8541
  
  gg_object$data$abs_diff_base_sim[762:792] <-
    overview$dif_vs_base[overview$POSTNR_TXT==8240]
  gg_object$data$postcode[762:792] <- 8240
  
  gg_object$data$abs_diff_base_sim[793:816] <-
    overview$dif_vs_base[overview$POSTNR_TXT==8210]
  gg_object$data$postcode[793:816] <- 8210
  
  gg_object$data$abs_diff_base_sim[817:846] <- 
    overview$dif_vs_base[overview$POSTNR_TXT==8220]
  gg_object$data$postcode[817:846] <- 8220
  
  return(gg_object)
}

#Put in original number of households with non-western immigrants in each postcode 
add_original <- function(gg_object, total){
  
  gg_object$data$acutal_number_households <- NA
  gg_object$data$postcode <- NA
  gg_object$data$acutal_number_households[1:33] <-
   total$`Total non-western households`[total$POSTNR_TXT==8380]
  gg_object$data$postcode[1:33] <- 8380
  
  gg_object$data$acutal_number_households[34:64] <-
    total$`Total non-western households`[total$POSTNR_TXT==8310]
  gg_object$data$postcode[34:64] <- 8310
  
  gg_object$data$acutal_number_households[65:125] <-
    total$`Total non-western households`[total$POSTNR_TXT==8340]
  gg_object$data$postcode[65:125] <- 8340
  
  gg_object$data$acutal_number_households[126:170] <-
    total$`Total non-western households`[total$POSTNR_TXT==8270]
  gg_object$data$postcode[126:170] <- 8270
  
  gg_object$data$acutal_number_households[171:200] <- 
    total$`Total non-western households`[total$POSTNR_TXT==8330]
  gg_object$data$postcode[171:200] <- 8330
  
  gg_object$data$acutal_number_households[201:243] <- 
    total$`Total non-western households`[total$POSTNR_TXT==8530]
  gg_object$data$postcode[201:243] <- 8530
  
  gg_object$data$acutal_number_households[244:267] <- 
    total$`Total non-western households`[total$POSTNR_TXT==8320]
  gg_object$data$postcode[244:267] <- 8320 
  
  gg_object$data$acutal_number_households[245:296] <-
    total$`Total non-western households`[total$POSTNR_TXT==8462]
  gg_object$data$postcode[245:296] <- 8462 
  
  gg_object$data$acutal_number_households[297:321] <- 
     total$`Total non-western households`[total$POSTNR_TXT==8230]
  gg_object$data$postcode[297:321] <-8230
  
  gg_object$data$acutal_number_households[322:353] <-
    total$`Total non-western households`[total$POSTNR_TXT==8381]
  gg_object$data$postcode[322:353] <-8381
  
  
  gg_object$data$acutal_number_households[354:395] <-
     total$`Total non-western households`[total$POSTNR_TXT==8250]
  gg_object$data$postcode[354:395] <- 8250
    
  gg_object$data$acutal_number_households[396:422] <-
    total$`Total non-western households`[total$POSTNR_TXT==8361]
  gg_object$data$postcode[396:422] <- 8361
  
  gg_object$data$acutal_number_households[423:462] <- 
    total$`Total non-western households`[total$POSTNR_TXT==8260]
  gg_object$data$postcode[423:462] <- 8260
  
  gg_object$data$acutal_number_households[463:544] <- 
    total$`Total non-western households`[total$POSTNR_TXT==8000]
  gg_object$data$postcode[463:544] <- 8000
  
  gg_object$data$acutal_number_households[545:579] <-
    total$`Total non-western households`[total$POSTNR_TXT==8355]
  gg_object$data$postcode[545:579] <- 8355
  
  gg_object$data$acutal_number_households[580:608] <-
    total$`Total non-western households`[total$POSTNR_TXT==8520]
  gg_object$data$postcode[580:608] <- 8520
  
  gg_object$data$acutal_number_households[609:651] <-
    total$`Total non-western households`[total$POSTNR_TXT==8471]
  gg_object$data$postcode[609:651] <- 8471
    
  gg_object$data$acutal_number_households[652:684] <-
    total$`Total non-western households`[total$POSTNR_TXT==8200]
  gg_object$data$postcode[652:684] <- 8200
    
  gg_object$data$acutal_number_households[685:737] <-
    total$`Total non-western households`[total$POSTNR_TXT==8541]
  gg_object$data$postcode[685:737] <- 8541
    
  gg_object$data$acutal_number_households[738:761] <- 
    total$`Total non-western households`[total$POSTNR_TXT==8541] 
  gg_object$data$postcode[738:761] <- 8541
  
  gg_object$data$acutal_number_households[762:792] <-
    total$`Total non-western households`[total$POSTNR_TXT==8240]
  gg_object$data$postcode[762:792] <- 8240
  
  gg_object$data$acutal_number_households[793:816] <-
    total$`Total non-western households`[total$POSTNR_TXT==8210]
  gg_object$data$postcode[793:816] <- 8210
  
  gg_object$data$acutal_number_households[817:846] <- 
    total$`Total non-western households`[total$POSTNR_TXT==8220]
  gg_object$data$postcode[817:846] <- 8220
  
  return(gg_object)
}


```


Number of immigrant households in each postcode: Original vs. base simulation 
```{r}
## Import aarhus data 
post <- readOGR("postalcodes_aarhus.shp")

###################################### GG Base Simulation #################################
#Import results 
overview_1 <- read.csv("results_base_1.csv")
colnames(overview_1)[1] <- "POSTNR_TXT" # Making sure the column names are identical for merge
#add the extra part of postcode
overview_1 <- rbind(overview_1[1:19,], overview_1[19,], overview_1[20:22,])

# Make overview dataframe in same order as plotorder in post 
overview_1$group <- seq(1:23)
overview_1 <- overview_1[match(post@plotOrder, overview_1$group),]
overview_1$group <- seq(1:23) # Making the group variable identical to the one in gg object
row.names(overview_1) <- seq(1:23)
overview_1[23,1] <- 8472 # Change name of extra postcode so it can merge 

post_merge <- sp::merge(post, overview_1, by = "POSTNR_TXT")

# Add in postcode numbers 
shp_df <- broom::tidy(post_merge, region = "POSTNR_TXT")
lapply(shp_df, class)
cnames <- aggregate(cbind(long, lat) ~ id, data=shp_df, FUN=mean)

#Changing positions of postcode names that are not on the borders 
cnames[1,2] <- cnames[1,2]-sd(shp_df$long[shp_df$id==8000])
cnames[7,2] <- cnames[7,2]-sd(shp_df$long[shp_df$id==8250])
cnames[8,3] <- cnames[8,3]+sd(shp_df$lat[shp_df$id==8260])/2
# Put in the data from simulation to be added as color gradient 
test_gg <- ggplot(data = post)
test_gg <- add_sim_to_gg(test_gg, overview_1)
test_gg <- add_abs_diff_to_base_gg(test_gg, overview_1) 

################################### Plot number of immigrants ############################
#log transform number of immigrants so variability is visible 
test_gg$data$log_number_immigrants <- ifelse(test_gg$data$number_immigrants>0, log(test_gg$data$number_immigrants), test_gg$data$number_immigrants)

base_number <-  test_gg + geom_polygon(aes(x = long, y = lat, group = group, fill = log_number_immigrants), col="black") + 
  scale_fill_gradientn(colours = c( "#ffffe5", "#fff7bc", "#fee391", "#fec44f", "#fe9929", "#ec7014", "#cc4c02", "#993404", "#662506")) + 
  theme_void() + 
  geom_text(data = cnames, aes(x = long, y = lat, label = id), size = 4) + 
  labs(title = "Number of Migrant Households in Each Postcode in Base Simulation \nLog-Transformed", fill = "Log-Transformed \nNumber of Households") + 
    theme(plot.title = element_text(6)) + plot_annotation(tag_levels ="A")

################################## Plot Abs difference from original ######################
#log transform absolute difference in immigrants so variability is visible 
test_gg$data$log_abs_diff_real_sim <- ifelse(test_gg$data$abs_diff_real_sim>0, log(test_gg$data$abs_diff_real_sim), test_gg$data$abs_diff_real_sim)

base_diff <- test_gg + geom_polygon(aes(x = long, y = lat, group = group, fill = log_abs_diff_real_sim), col="black") + 
  scale_fill_gradientn(colours = c( "#ffffe5", "#fff7bc", "#fee391", "#fec44f", "#fe9929", "#ec7014", "#cc4c02", "#993404", "#662506")) +
  theme_void() + 
  geom_text(data = cnames, aes(x = long, y = lat, label = id), size = 4, color = "black") +
  labs(title = "Absolute Difference Between Real Number of Migrant Households and Simulated \nLog-transformed", fill = "Log-transformed \nDifferences") 

################################## Original number plot ###################################
original_number <- read_csv("total_over_under_18.csv")
#add POSTNR_TXT to total df
colnames(original_number)[1] <- c("POSTNR_TXT")

test_gg <- add_original(test_gg, original_number)
#log transform original number of households
test_gg$data$log_acutal_number_households <- ifelse(test_gg$data$acutal_number_households>0, log(test_gg$data$acutal_number_households), test_gg$data$acutal_number_households)

original <- test_gg + geom_polygon(aes(x = long, y = lat, group = group, fill = log_acutal_number_households), col="black") + 
  scale_fill_gradientn(colours = c( "#ffffe5", "#fff7bc", "#fee391", "#fec44f", "#fe9929", "#ec7014", "#cc4c02", "#993404", "#662506")) + 
  theme_void() + 
  geom_text(data = cnames, aes(x = long, y = lat, label = id), size = 4) + 
  labs(title = "Actual Number of Migrant Households In Postcodes", fill = "Log-transformed \nNumber of Households")


####################################### Arrange in grid #################################
#grid.arrange(original, base_number, base_diff)
```

Arranging: Original + base simulation 
```{r}
original/base_number/base_diff + plot_annotation(tag_levels = "a") 
#900X1200


```



Number of households in each postcode: Postcodes (8210 + 8220) restricted for 5 % of low income group (integrationsydelse initiative in Ghettoplan)
```{r}
## Import aarhus data 
post <- readOGR("postalcodes_aarhus.shp")

###################################### GG Int Simulation #################################
#Import results 
overview_int <- read.csv("results_int_1.csv")
colnames(overview_int)[1] <- "POSTNR_TXT" # Making sure the column names are identical for merge
#add the extra part of postcode
overview_int <- rbind(overview_int[1:19,], overview_int[19,], overview_int[20:22,])

# Make overview dataframe in same order as plotorder in post 
overview_int$group <- seq(1:23)
overview_int <- overview_int[match(post@plotOrder, overview_int$group),]
overview_int$group <- seq(1:23) # Making the group variable identical to the one in gg object
row.names(overview_int) <- seq(1:23)
overview_int[23,1] <- 8472 # Change name of extra postcode so it can merge 

# Add in postcode numbers
post_merge <- sp::merge(post, overview_int, by = "POSTNR_TXT")

shp_df <- broom::tidy(post_merge, region = "POSTNR_TXT")
lapply(shp_df, class)
cnames <- aggregate(cbind(long, lat) ~ id, data=shp_df, FUN=mean)

#Changing positions of postcode names that are on the borders 
cnames[1,2] <- cnames[1,2]-sd(shp_df$long[shp_df$id==8000])
cnames[7,2] <- cnames[7,2]-sd(shp_df$long[shp_df$id==8250])
cnames[8,3] <- cnames[8,3]+sd(shp_df$lat[shp_df$id==8260])/2

# Put in the data from simulation to be added as color gradient 
gg_int <- ggplot(data = post)
gg_int <- add_sim_to_gg(gg_int, overview_int)
gg_int <- add_abs_diff_to_rest_gg(gg_int, overview_int)

# plot with log transformed number of households in each postcode 
#Log-transform 
gg_int$data$log_number_immigrants <- ifelse(gg_int$data$number_immigrants>0, log(gg_int$data$number_immigrants), gg_int$data$number_immigrants)

int_number <- gg_int + geom_polygon(aes(x = long, y = lat, group = group, fill = log_number_immigrants), col="black") + 
  scale_fill_gradientn(colours = c( "#ffffe5", "#fff7bc", "#fee391", "#fec44f", "#fe9929", "#ec7014", "#cc4c02", "#993404", "#662506")) +
  theme_void() + 
  geom_text(data = cnames, aes(x = long, y = lat, label = id), size = 4) + 
  labs(title = "Number of Migrant Households in Postcodes in Int-benefit Simulation \nLog-transformed", fill = "Log-Transformed \nNumber of Households")+ theme(plot.title = element_text(6))


# Plot with absolute difference between integrationsydelse simulation and base simulation. Numbers are log-transformed
gg_int$data$log_abs_diff_base_sim <- ifelse(gg_int$data$abs_diff_base_sim>0, log(gg_int$data$abs_diff_base_sim), gg_int$data$abs_diff_base_sim)

int_difference <- gg_int + geom_polygon(aes(x = long, y = lat, group = group, fill = log_abs_diff_base_sim), col="black") + 
  scale_fill_gradientn(colours = c( "#ffffe5", "#fff7bc", "#fee391", "#fec44f", "#fe9929", "#ec7014", "#cc4c02", "#993404", "#662506")) +
  theme_void() + 
  geom_text(data = cnames, aes(x = long, y = lat, label = id), size = 4) + 
  labs(title = "Absolute Difference Between Number of Migrant Households in \nBase Simulation and Int-Benefit Restriction Simulation \nLog-transformed", fill = "Log-Transformed \ndifference")+ theme(plot.title = element_text(6))

```


Number of households in each postcode: Postcodes (8210 + 8220) removed from list of possible postcodes (Tearing down buildings initiative in Ghettoplan)
```{r}
## Import aarhus data 
post <- readOGR("postalcodes_aarhus.shp")

#################################### GG Build Simulation #################################
#Import results 
overview_build <- read.csv("results_build_1.csv")
colnames(overview_build)[1] <- "POSTNR_TXT" # Making sure the column names are identical for merge
#add the extra part of postcode
overview_build <- rbind(overview_build[1:19,], overview_build[19,], overview_build[20:22,])

# Make overview dataframe in same order as plotorder in post 
overview_build$group <- seq(1:23)
overview_build <- overview_build[match(post@plotOrder, overview_build$group),]
overview_build$group <- seq(1:23) # Making the group variable identical to the one in gg object
row.names(overview_build) <- seq(1:23)
overview_build[23,1] <- 8472 # Change name of extra postcode so it can merge 

# Add in postcode numbers
post_merge <- sp::merge(post, overview_build, by = "POSTNR_TXT")

shp_df <- broom::tidy(post_merge, region = "POSTNR_TXT")
lapply(shp_df, class)
cnames <- aggregate(cbind(long, lat) ~ id, data=shp_df, FUN=mean)

#Changing positions of postcode names that are on the borders 
cnames[1,2] <- cnames[1,2]-sd(shp_df$long[shp_df$id==8000])
cnames[7,2] <- cnames[7,2]-sd(shp_df$long[shp_df$id==8250])
cnames[8,3] <- cnames[8,3]+sd(shp_df$lat[shp_df$id==8260])/2
# Put in the data from simulation to be added as color gradient 
gg_build <- ggplot(data = post)
gg_build <- add_sim_to_gg(gg_build, overview_build)
gg_build <- add_abs_diff_to_rest_gg(gg_build, overview_build)

#Plot showing the number of immigrants households in each postcode. Log transformed 
# log transform 
gg_build$data$log_number_immigrants <- ifelse(gg_build$data$number_immigrants>0, log(gg_build$data$number_immigrants), gg_build$data$number_immigrants)

build_number <- gg_build + geom_polygon(aes(x = long, y = lat, group = group, fill = log_number_immigrants), col="black") + 
  scale_fill_gradientn(colours = c( "#ffffe5", "#fff7bc", "#fee391", "#fec44f", "#fe9929", "#ec7014", "#cc4c02", "#993404", "#662506")) +
  theme_void() + 
  geom_text(data = cnames, aes(x = long, y = lat, label = id), size = 4) + 
  labs(title = "Number of Migrant Households in Postcodes in Demolishing Buildings Simulation \nLog-transformed", fill = "Log-Transformed \nNumber of Households")+ theme(plot.title = element_text(6))


#Plot showing the absolute difference between the number of immigrants households in each postcode in the build simulation and the base simulation. Log transformed 
# log transform 
gg_build$data$log_abs_diff_base_sim <- ifelse(gg_build$data$abs_diff_base_sim>0, log(gg_build$data$abs_diff_base_sim), gg_build$data$abs_diff_base_sim)

build_difference <- gg_build + geom_polygon(aes(x = long, y = lat, group = group, fill = log_abs_diff_base_sim), col="black") + 
  scale_fill_gradientn(colours = c( "#ffffe5", "#fff7bc", "#fee391", "#fec44f", "#fe9929", "#ec7014", "#cc4c02", "#993404", "#662506")) +
  theme_void() + 
  geom_text(data = cnames, aes(x = long, y = lat, label = id), size = 4) + 
  labs(title = "Absolute Difference Between Number of Migrant Households in \nBase Simulation and Demolishing Buildings Simulation \nLog-transformed", fill = "Log-Transformed \ndifference")+ theme(plot.title = element_text(6))

```



Arranging difference plots together
```{r}
base_number/int_difference/build_difference + plot_annotation(tag_levels = "a")  
#900X1200


```




Distribution of agent types in each postcode: 
Base_kids_high 
```{r}
## Import aarhus data 
post <- readOGR("postalcodes_aarhus.shp")

############################ GG base_kids_high Simulation ############################
#Import results 
overview_kids_high <- read.csv("results_base_kids_high.csv")
colnames(overview_kids_high)[1] <- "POSTNR_TXT" # Making sure the column names are identical for merge
#add the extra part of postcode
overview_kids_high <- rbind(overview_kids_high[1:19,], overview_kids_high[19,], overview_kids_high[20:22,])

# Make overview dataframe in same order as plotorder in post 
overview_kids_high$group <- seq(1:23)
overview_kids_high <- overview_kids_high[match(post@plotOrder, overview_kids_high$group),]
overview_kids_high$group <- seq(1:23) # Making the group variable identical to the one in gg object
row.names(overview_kids_high) <- seq(1:23)
overview_kids_high[23,1] <- 8472 # Change name of extra postcode so it can merge 

# Add in postcode numbers
post_merge <- sp::merge(post, overview_kids_high, by = "POSTNR_TXT")

shp_df <- broom::tidy(post_merge, region = "POSTNR_TXT")
lapply(shp_df, class)
cnames <- aggregate(cbind(long, lat) ~ id, data=shp_df, FUN=mean)

#Changing positions of postcode names that are on the borders 
cnames[1,2] <- cnames[1,2]-sd(shp_df$long[shp_df$id==8000])
cnames[7,2] <- cnames[7,2]-sd(shp_df$long[shp_df$id==8250])
cnames[8,3] <- cnames[8,3]+sd(shp_df$lat[shp_df$id==8260])/2
# Put in the data from simulation to be added as color gradient 
gg_kids_high <- ggplot(data = post)
gg_kids_high <- add_sim_to_gg(gg_kids_high, overview_kids_high)

#Plot showing the number of immigrant households in each postcode. Log transformed 
# log transform
gg_kids_high$data$log_number_immigrants <- ifelse(gg_kids_high$data$number_immigrants>0, log(gg_kids_high$data$number_immigrants), gg_kids_high$data$number_immigrants) 

numb_kids_high <- gg_kids_high + geom_polygon(aes(x = long, y = lat, group = group, fill = log_number_immigrants), col="black") + 
  scale_fill_gradientn(colours = c( "#ffffe5", "#fff7bc", "#fee391", "#fec44f", "#fe9929", "#ec7014", "#cc4c02", "#993404", "#662506")) +
  theme_void() + 
  geom_text(data = cnames, aes(x = long, y = lat, label = id), size = 4) + 
  labs(title = "Number of Migrant Households in Each Postcode \nAgent Type: With Kids-High Income", fill = "Log-Transformed \nNumber of Households")+ theme(plot.title = element_text(10))



```

Base_no_high
```{r}
## Import aarhus data 
post <- readOGR("postalcodes_aarhus.shp")

############################ GG base_kids_high Simulation ############################
#Import results 
overview_no_high <- read.csv("results_base_no_high.csv")
colnames(overview_no_high)[1] <- "POSTNR_TXT" # Making sure the column names are identical for merge
#add the extra part of postcode
overview_no_high <- rbind(overview_no_high[1:19,], overview_no_high[19,], overview_no_high[20:22,])

# Make overview dataframe in same order as plotorder in post 
overview_no_high$group <- seq(1:23)
overview_no_high <- overview_no_high[match(post@plotOrder, overview_no_high$group),]
overview_no_high$group <- seq(1:23) # Making the group variable identical to the one in gg object
row.names(overview_no_high) <- seq(1:23)
overview_no_high[23,1] <- 8472 # Change name of extra postcode so it can merge 

# Add in postcode numbers
post_merge <- sp::merge(post, overview_no_high, by = "POSTNR_TXT")

shp_df <- broom::tidy(post_merge, region = "POSTNR_TXT")
lapply(shp_df, class)
cnames <- aggregate(cbind(long, lat) ~ id, data=shp_df, FUN=mean)

#Changing positions of postcode names that are on the borders 
cnames[1,2] <- cnames[1,2]-sd(shp_df$long[shp_df$id==8000])
cnames[7,2] <- cnames[7,2]-sd(shp_df$long[shp_df$id==8250])
cnames[8,3] <- cnames[8,3]+sd(shp_df$lat[shp_df$id==8260])/2
# Put in the data from simulation to be added as color gradient 
gg_no_high <- ggplot(data = post)
gg_no_high <- add_sim_to_gg(gg_no_high, overview_no_high)

#Plot showing the number of immigrant households in each postcode. Log transformed 
# log transform
gg_no_high$data$log_number_immigrants <- ifelse(gg_no_high$data$number_immigrants>0, log(gg_no_high$data$number_immigrants), gg_no_high$data$number_immigrants) 

numb_no_high <- gg_no_high + geom_polygon(aes(x = long, y = lat, group = group, fill = log_number_immigrants), col="black") + 
  scale_fill_gradientn(colours = c( "#ffffe5", "#fff7bc", "#fee391", "#fec44f", "#fe9929", "#ec7014", "#cc4c02", "#993404", "#662506")) +
  theme_void() + 
  geom_text(data = cnames, aes(x = long, y = lat, label = id), size = 4) + 
  labs(title = "Number of Migrant Households in Each Postcode \nAgent Type: No Kids-High Income", fill = "Log-Transformed \nNumber of Households")+ theme(plot.title = element_text(10))



```

Base_kids_low 
```{r}
## Import aarhus data 
post <- readOGR("postalcodes_aarhus.shp")

############################ GG base_kids_high Simulation ############################
#Import results 
overview_kids_low <- read.csv("results_base_kids_low.csv")
colnames(overview_kids_low)[1] <- "POSTNR_TXT" # Making sure the column names are identical for merge
#add the extra part of postcode
overview_kids_low <- rbind(overview_kids_low[1:19,], overview_kids_low[19,], overview_kids_low[20:22,])

# Make overview dataframe in same order as plotorder in post 
overview_kids_low$group <- seq(1:23)
overview_kids_low <- overview_kids_low[match(post@plotOrder, overview_kids_low$group),]
overview_kids_low$group <- seq(1:23) # Making the group variable identical to the one in gg object
row.names(overview_kids_low) <- seq(1:23)
overview_kids_low[23,1] <- 8472 # Change name of extra postcode so it can merge 

# Add in postcode numbers
post_merge <- sp::merge(post, overview_kids_low, by = "POSTNR_TXT")

shp_df <- broom::tidy(post_merge, region = "POSTNR_TXT")
lapply(shp_df, class)
cnames <- aggregate(cbind(long, lat) ~ id, data=shp_df, FUN=mean)

#Changing positions of postcode names that are on the borders 
cnames[1,2] <- cnames[1,2]-sd(shp_df$long[shp_df$id==8000])
cnames[7,2] <- cnames[7,2]-sd(shp_df$long[shp_df$id==8250])
cnames[8,3] <- cnames[8,3]+sd(shp_df$lat[shp_df$id==8260])/2
# Put in the data from simulation to be added as color gradient 
gg_kids_low <- ggplot(data = post)
gg_kids_low <- add_sim_to_gg(gg_kids_low, overview_kids_low)

#Plot showing the number of immigrant households in each postcode. Log transformed 
# log transform
gg_kids_low$data$log_number_immigrants <- ifelse(gg_kids_low$data$number_immigrants>0, log(gg_kids_low$data$number_immigrants), gg_kids_low$data$number_immigrants) 

numb_kids_low <- gg_kids_low + geom_polygon(aes(x = long, y = lat, group = group, fill = log_number_immigrants), col="black") + 
  scale_fill_gradientn(colours = c( "#ffffe5", "#fff7bc", "#fee391", "#fec44f", "#fe9929", "#ec7014", "#cc4c02", "#993404", "#662506")) +
  theme_void() + 
  geom_text(data = cnames, aes(x = long, y = lat, label = id), size = 4) + 
  labs(title = "Number of Migrant Households in Each Postcode \nAgent Type: With Kids-Low Income", fill = "Log-Transformed \nNumber of Households") + theme(plot.title = element_text(10))

```

Base_no_low 
```{r}
## Import aarhus data 
post <- readOGR("postalcodes_aarhus.shp")

############################ GG base_kids_high Simulation ############################
#Import results 
overview_no_low <- read.csv("results_base_no_low.csv")
colnames(overview_no_low)[1] <- "POSTNR_TXT" # Making sure the column names are identical for merge
#add the extra part of postcode
overview_no_low <- rbind(overview_no_low[1:19,], overview_no_low[19,], overview_no_low[20:22,])

# Make overview dataframe in same order as plotorder in post 
overview_no_low$group <- seq(1:23)
overview_no_low <- overview_no_low[match(post@plotOrder, overview_no_low$group),]
overview_no_low$group <- seq(1:23) # Making the group variable identical to the one in gg object
row.names(overview_no_low) <- seq(1:23)
overview_no_low[23,1] <- 8472 # Change name of extra postcode so it can merge 

# Add in postcode numbers
post_merge <- sp::merge(post, overview_no_low, by = "POSTNR_TXT")

shp_df <- broom::tidy(post_merge, region = "POSTNR_TXT")
lapply(shp_df, class)
cnames <- aggregate(cbind(long, lat) ~ id, data=shp_df, FUN=mean)

#Changing positions of postcode names that are on the borders 
cnames[1,2] <- cnames[1,2]-sd(shp_df$long[shp_df$id==8000])
cnames[7,2] <- cnames[7,2]-sd(shp_df$long[shp_df$id==8250])
cnames[8,3] <- cnames[8,3]+sd(shp_df$lat[shp_df$id==8260])/2

# Put in the data from simulation to be added as color gradient 
gg_no_low <- ggplot(data = post)
gg_no_low <- add_sim_to_gg(gg_no_low, overview_no_low)

#Plot showing the number of immigrant households in each postcode. Log transformed 
# log transform
gg_no_low$data$log_number_immigrants <- ifelse(gg_no_low$data$number_immigrants>0, log(gg_no_low$data$number_immigrants), gg_no_low$data$number_immigrants) 

numb_no_low <- gg_no_low + geom_polygon(aes(x = long, y = lat, group = group, fill = log_number_immigrants), col="black") + 
  scale_fill_gradientn(colours = c( "#ffffe5", "#fff7bc", "#fee391", "#fec44f", "#fe9929", "#ec7014", "#cc4c02", "#993404", "#662506")) +
  theme_void() + 
  geom_text(data = cnames, aes(x = long, y = lat, label = id), size = 4) + 
  labs(title = "Number of Migrant Households in Each Postcode \nAgent Type: No Kids-Low Income", fill = "Log-Transformed \nNumber of Households") + theme(plot.title = element_text(10))


```


Arranging the plots in a grid
```{r}
(numb_kids_high+numb_kids_low)/(numb_no_high+numb_no_low) + plot_annotation(tag_levels = "a") 
#1500X1100

```


Table of numbers of immigrants households in each postcode: Original vs. Base vs. Int vs. Build 
```{r}
#Sort like original numbers
overview_1_sorted <- overview_1[match(original_number$POSTNR_TXT, overview_1$POSTNR_TXT),]
overview_build_sorted <- overview_build[match(original_number$POSTNR_TXT, overview_build$POSTNR_TXT),]
overview_int_sorted <- overview_int[match(original_number$POSTNR_TXT, overview_int$POSTNR_TXT),]


table_of_numbers <- data.frame(
  Postcode = original_number$POSTNR_TXT,
  actual_number_households = original_number$`Total non-western households`,
  base_simulation_diff_real = original_number$`Total non-western households`- overview_1_sorted$base_line,
  number_of_households_base = overview_1_sorted$base_line,
  int_simulation_diff_base = overview_1_sorted$base_line-overview_int_sorted$base_line,
  build_simulaion_diff_base = overview_1_sorted$base_line-overview_build_sorted$base_line)

in_total <- c("In total",
              sum(abs(original_number$`Total non-western households`)),
              sum(abs(overview_1_sorted$dif_vs_real)), 
              sum(abs(overview_1_sorted$base_line)),
              sum(abs(overview_int_sorted$dif_vs_base)), 
              sum(abs(overview_build_sorted$dif_vs_base)))


table_of_numbers <- rbind(table_of_numbers, in_total)

#Change the column names 
colnames(table_of_numbers) <- c("Postcode", "Real Number of \nMigrant Households", "Base Simulation: Difference \nbetween Base Sim and Real Number", "Number of Households in \nBase Simulation",  "Int-Benefit Simulation: Difference \nbetween Int-Benefit and Base Sim", "Building Simulation: Difference \nbetween Building and Base Sim")

#Save as png 
# png("table_of_numbers.png", height = 50*nrow(table_of_numbers), width = 200*ncol(table_of_numbers))
# grid.table(table_of_numbers)
# dev.off()
```

